---
runtime: shiny
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Here are two Shiny widgets



## PMS Study

This is the data processing html for the PMS study

```{r libraries, include = FALSE}
# we will first write some pseudocode to describe what we want to do
#upload files
#find best linear model to represent data with AI

#     PSS ~ PMSScore*Moment + (1|Subject)
# 
#     PSS deppendent variablle
#     pMS = 1 geen PMS
#     keer moment: moment v afname
#     1 out of subject: random effect toevoegen
#     straks factoren vd PMS score en van moment: hoeveel levels? 
#       formules van doen
#     laten weten welke formule beste
#     

    
#### Settings & Packages #### -----------------------------------------------------
rm(list = ls())
options(contrasts = c("contr.sum","contr.poly")) #use this for the p value of the t test
library(lme4)
library(lmerTest)
library(effects)
library(dplyr)
library(car)
library(emmeans)
library(fitdistrplus)
library(dplyr)
library(car)
# library(MuMIn)
library(ggplot2)
library(ggstatsplot)
library(ggsignif)
library(gridExtra)
library(tidyverse)
library(ggeffects)
library(pander)
# library(viridis)
library (yarrr)
library(knitr)
recode <- dplyr::recode
# Suppress summarize info
options(dplyr.summarise.inform = FALSE)
count <- dplyr::count 
# set the theme to theme_bw for all ggplot2 figures
theme_set(theme_bw())
# create folder to save figures
if (!dir.exists("figures")) dir.create("figures")


# General settings
nAGQ = 0 # When writing code, set to 0, when getting final results, set to 1
```


```{r load-data, echo=FALSE, results='asis'}
#### IMPORT DATA & INSPECTION #### -------------------------------------------------------------
knitr::opts_knit$set(root.dir = dirname(rstudioapi::getActiveDocumentContext()$path))# Set working directory to current directory
# setwd("C:\Users\ASUSTeK\OneDrive\2021-2022\internship\projects")
data <- read.csv("Data/allPMSdata.csv", header=TRUE)
# data <- read.table("Data/allPMSdata.csv",sep="\t", header=TRUE)


# from wide to long
#check if subject column is a facctor
#str(data)
#head(data)
# data <-as.numeric(data)
data$Subject <- factor(data$ID)
#typeof(data$Subject)


#we make a new variable that has value 1 for the first TestMoment and 2 for the second TestMoment
#These moments were counterbalanced
#when the order was B-A and the moment is B, this means it is the first test moment
#and vice versa for A-B and moment A. 

# TestMoment 1 == Follicular phase
# TestMoment 2 == Luteal phase
data$TestMoment[data$Order == "A-B" & data$Moment == "A"] = 1
data$TestMoment[data$Order == "B-A" & data$Moment == "A"] = 2
data$TestMoment[data$Order == "A-B" & data$Moment == "B"] = 2
data$TestMoment[data$Order == "B-A" & data$Moment == "B"] = 1
#check if there are still values missing (NA)
#sum(is.na(data$TestMoment))

# new variable PMSSCORE NEW iedereen pms 0 ook 0 iedereen die 1 OF 2 heeft wordt 1, 
data$PMSScoreNew[data$PMSScore==0] = 'noPMS'
data$PMSScoreNew[data$PMSScore==1] = 'PMS'
data$PMSScoreNew[data$PMSScore==2] = 'PMS'
#sum(is.na(data$PMSScoreNew))


# Check whether R recognizes the variable types correctly
#we make factors of the independable variables

data$PMSScore <- factor(data$PMSScore)
data$PMSScoreNew <- factor(data$PMSScoreNew)

data$Moment <- factor(data$TestMoment) # This removes "A and B", A == 1, B == 2 now

# Exclude data?
dataBig = data # Saved all the data here
data = data[, -which(names(data) == "X" | names(data) == "Stimulus" | names(data) == "Valence" | names(data) == "Arousal" | names(data) == "rt")]
data = distinct(data)

# exclude everyone on the pill/copper spiral/other: only those with Natural Contraception are left included
data<-subset(data, Contraception!="Pill" & Contraception!="other" & Contraception!="Cop. Coil" & Contraception!="Hor.Coil")

data <- subset(data,BSRI!=0 ) #remove datapoints where BSRI = 0

# Define the formula for the model & check which model fits the data best

data_temp <- data #to get back to

```
## Choose a Formula

```{r echo=FALSE}


selectInput("formula_choice", label="Which Formula:",
            choices= c('PSS ~ TestMoment', 'BSRI ~ TestMoment', 'PSS~PMSScoreNew*TestMoment'),
            selected='PSS ~ TestMoment') # puts the choices in the first element which is accessed via input$formula_choice

```

```{r echo=FALSE}

```
## ANOVA

```{r echo=FALSE}

mainPanel(
   tabsetPanel(type = "tab",
                tabPanel("Model", verbatimTextOutput("AD")),
               tabPanel("Visualization", plotOutput("VP"))
       )
)

output$AD <- renderPrint({
  Formula <- as.formula(paste0(input$formula_choice, ' + (1|Subject)'))
    d0.1 <- lmer(input$Formula,data=data)
    d0.2 <- glmer(input$Formula,data=data, family = gaussian(link = "inverse"),glmerControl(optimizer= "bobyqa", optCtrl = list(maxfun = 100000)),nAGQ=nAGQ)
    d0.3 <- glmer(input$Formula,data=data, family = gaussian(link = "log"),glmerControl(optimizer= "bobyqa", optCtrl = list(maxfun = 100000)),nAGQ=nAGQ)
  
    d0.4 <- glmer(input$Formula,data=data, family = Gamma(link = "identity"),glmerControl(optimizer= "bobyqa", optCtrl = list(maxfun = 100000)),nAGQ=nAGQ)
    d0.5 <- glmer(input$Formula,data=data, family = Gamma(link = "inverse"),glmerControl(optimizer= "bobyqa", optCtrl = list(maxfun = 100000)),nAGQ=nAGQ)
    d0.6 <- glmer(input$Formula,data=data, family = Gamma(link = "log"),glmerControl(optimizer= "bobyqa", optCtrl = list(maxfun = 100000)),nAGQ=nAGQ)
  
    d0.7 <- glmer(input$Formula,data=data, family = inverse.gaussian(link = "identity"),glmerControl(optimizer= "bobyqa", optCtrl = list(maxfun = 100000)),nAGQ=nAGQ)
    d0.8 <- glmer(input$Formula,data=data, family = inverse.gaussian(link = "inverse"),glmerControl(optimizer= "bobyqa", optCtrl = list(maxfun = 100000)),nAGQ=nAGQ)
    d0.9 <- glmer(input$Formula,data=data, family = inverse.gaussian(link = "log"),glmerControl(optimizer= "bobyqa", optCtrl = list(maxfun = 100000)),nAGQ=nAGQ)
  
    modelNames = c(d0.1,d0.2,d0.3,d0.4,d0.5,d0.6,d0.7,d0.8,d0.9)
  
  # Remove the models that produced errors in the line below, the one with the lowest value is the best fitting model
 #  tabel <- cbind(AIC(d0.1), AIC(d0.2), AIC(d0.3), AIC(d0.4), AIC(d0.5), AIC(d0.6), AIC(d0.7), AIC(d0.8), AIC(d0.9))
 #  #show table in html
 # # renderTable(tabel,, striped= TRUE)
 #  chosenModel = modelNames[which(tabel == min(tabel))]
 #  
 #  print(Anova(chosenModel))
 #  
 #  print(summary(Anova(chosenModel, data=data)))
})

# ```
# output$AD <- renderPrint({
#   summary(Anova(as.formula(chosenModel), data=data))
# })
```

## Now we get a plot!

```{r echo=FALSE}

renderPrint(input$formula_choice)
  # Plotting
  dpi=600    #pixels per square inch
  # jpeg(paste0(plotPrefix, "Figure", "_", plotTitles[i], ".jpeg"), width=8*dpi, height=4*dpi, res=dpi)
  par(mfcol = c(1, 1))
  
renderPlot({
  pirateplot(
    formula= input$formula_choice,
    data=data,
    theme= 1,
    pal= "info",
    main= input$formula_choice,
    bean.f.o = .6, # Bean fill
    point.o = .3,  # Points
    inf.f.o = .7,  # Inference fill
    inf.b.o = .8,  # Inference border
    avg.line.o = 1,  # Average line
    bar.f.o = .5, # Bar
    inf.f.col = "white",  # Inf fill col
    inf.b.col = "black",  # Inf border col
    avg.line.col = "black",  # avg line col
    bar.f.col = gray(.8),  # bar filling color
    point.pch = 21,
    point.bg = "white",
    point.col = "black",
    point.cex = .7,
    xlab="",
  )
})

```



